\chapter{The biggest}

What is the biggest goal in life? I think it is to increase kindness in everything that surrounds us. First of all, kindness is about happiness of all the people. This includes many things, and every time life can give you the task, that you should know how to solve. You can do good in the details, you can think about doing something big and good, but these are all parts of the same thing. Much of it starts in the details. It is brought up during childhood in the family.

A child loves his mother and his father, siblings, family, home. His affection gradually grows, he starts caring for his school, his village, his city, his whole country. Now that is a big and deep feeling, however one should not stop there, a human should love a human just being a human.

Be a patriot, not a nationalist. There's no need to hate every other family for the sake of loving your own. There's no need to hate other nations, because you are a patriot. There's a fundumental difference between patriotism and nationalism. The first is about loving your own country, and the second spurs hatred to all the other ones.

A big goal of the good starts with the lesser thing -- willingness to help your relatives. The further this goal expands the wider range of problems it deals with.

It's like ripples on a pond. But the water ripples get weaker as they spread. But when love and friendship grow and expand, they get stonger and higher, and the man, their center, gets wiser.

Love shouldn't be careless, it ought to be smart. This means that love should be connected with the ability to spot out the flaws and fix them. Flaws in a man and people around alike. It must connected with wisdom and judgement neccesary to seperate the necessary from empty and fase. Love mustn't be blind. Blind delight (I can't even call it love) can lead to horrifying results. A mother that admires her child and encourages the kid in all the deeds can raise an amoral libertin. Blind delight before Germany ("Germany above all" -- lyrics of one chauvinistic German song) led to the nazism, blind delight before Italy led to the fascism.

Wisdom is intelligence connected with kindness. Intelligence without kindness is cunning. Cunning gradually weakens and invariable, sooner or later, will turn against the hypocrite himself. That's why cunning has to hide itself. Wisdom is open and secure. It misleads no one, particularly the wise person. Wisdom brings you good name and stable happiness. It bring reliable happinness, the long one, and calm conscience, that is so valuable for an old man.

How to express that common string between these three positions: "Big in small", "Youth is all there's in life" and "The biggest"? I guess it can be expressed with one word, a possible slogan: "Commitment". Commitment to those big principles that should run one's life in big and small, commitment to the cloudless years of youth, commitment to your motherland in the broad sense and in the strict sense, commitment to your family, friends, city, country, people. In the end commitment is always the commitment to the right: the right and true, the right and just.
