\chapter{Life is the highest value}

"Inhale, exhale, inhale!" I hear the voice of the gymanstics' instructor: "To take a deep breath you need to exhale properly. Learn to exhale, to get rid of the 'used air'."

Life is first and foremost breathing. Spirit comes a Latin verb \texttt{spirtus}--to breathe.\footnote{It's the same story in Russian. \texttt{Дышать} is translated as to breathe, \texttt{душа} stands for soul. These words are cognate.} And dying means first of all stopping your breath. And since the old days people said that, when a person stops breathing, the spirit leaves the body. 

It can get "muggy" at home, and it can get "muggy" in a moral life. Breathe out all the petty troubles and all the routine hastiness, free yourself from things that limit your imagination and pressure soul, bar you from accepting life, its values and its beauty as they are.

A person ought to always think about the most important to ownself and others, getting away from all the empty worries.

We need to be open to people, tolerant, seek the best in them. Being able to look for and find the best features, just the good ones and the "unnoticed beauty" enriches you spiritually.

To spot beauty in nature, in a village, in a city, not to mention in a person, to see it through all the small barriers, it means to widen your horizon, expand your sphere of life.

That's the word I had been searching for a long time, sphere. At first I said to myself: "We need to expand boundaries of life". But life has no boundaries! It's not a land property, surrounded fenced by the boundaries. It's the same story with the phrase "to expand one's limits of life". "Widening your horizons" is much better. The word "eyesight" might work. All the things your eyes can see. But still it is limited by our "common knowledge". Life can't be bounded by our routine life. We ought to feel and notice things beyond our perception, have a "premonition" of a new thing to open sooner or later. Life is the highest value: life of a stranger, life of your own, animals' and plants' lives. Life in past, present and future. Life is infinitely deep. There's always something new, something that amazes with the beauty, the unexpected wisdom, the originality.