\chapter{What is the meaning of life?}

There're many ways to determine the purpose of your existence, but there must be some purpose, otherwise there's no life, only aimless vegetation.

You have to have principles in your life. Better even write them down in your diary, but only if the diary is "real", don't show it to anyone and write for yourself only.

But one rule in life should be common among all of us, same in everybody's purposes, prinicples and manners: live your life with dignity, so that you wouldn't be ashamed to remember it.

Dignity demands kindness, benevolence, being able not to be narrowly self-interested, truthfulness. A dignified person is a good friend and can find joy in helping others.

It is necessary to decline small and big pleasures for the sake of dignity. Better apologize and admit mistakes than equivocate and lie.

A lying man lies foremost to himself. He usually thinks that his lie is successful, but people recognize is and keep silence about it out of delicacy. It's always easy to see lying. People feel it, when they're lied to. But usualy there's no evidence, and even more oftenly they just don't want to get into this...

Nature had been working on human kind for many millions of years. I think that we ought to respect this creative, constructive effort of nature: we have to live our lives with honor and live them in such a way, that we don't leave our creator nature offended. Nature is constructive, it made us, that's why in our lives we should support this tendency of creativity and not any of the destructive things in the world. It is everyone's individual duty to determine how to apply this sentiment to one's own life. But live your life creating things and supporting creativity. Life is diverse and so is the process of making things. Our willingness to create should be diverse as our abilities and habits are. What do you think?

In this life there's some level of happinness that we use to start counting from, like a mean sea level.

Mean level. Well, it's everyone's duty to raise this mean level of happiness in life during all the deeds, big and small. And your own happiness is not to be ignored in this regard. But mainly people around you, those who are near to you, those whose level of happiness can be lifted so easily, without any worries. The duty is also about making happier your own country and the whole human kind in the end.

There're many ways to do that, but all of us can do something. If you can't solve political issues, these things alway raise level of hapinness, if handled wisely, you can lift it in your work environment, your school, for your friends and peers. Everyone has this opportunity.

Life is always creativity, but it doesn't mean that every single person is be born to be an artist, a ballerina or a scientist. Creativity can be created too. You can just create an air of kindness around you, a kind aura, as they say now. For example, one can bring feelings of suspicion and long silence or joy and light. This is art. Art is always continious. So life is infinite creativity. A man is born and leaves memory about himself. What kind of memory? I think, this question should bother people of all ages because we can leave at any moment. And it's very important what people will remember about you.